Temporal stability in human interaction networks: sector sizes, topological prominence and time activity

### 2015-10-06 paper.tex
terminada revisao dos resultados nos setores de erdos

The distribution of vertices in the hubs, intermediary, periphery Erd\"os sectors is remarkably stable along time, provided that a sufficiently large sample of 200 or more messages is considered. 
Moreover, the same distribution applies to the networks of all email lists analyzed,
as demonstrated in Figure~\ref{fig:sectIL} and in Section~\ref{si:frac} of the Supporting Information document. 
Activity is highly concentrated on the hubs, while a very large number of peripheral vertices contribute to only a fraction of the activity. This is expected for a system with a scale-free profile, as confirmed by the data in Table~\ref{autores} for the distribution of activity among participants.

Typically, $\approx [3-12]\%$ of the vertices are hubs, $\approx [15-45]\%$ are intermediary and $\approx [44-81]\%$ are peripheral, which is consistent with the literature~\cite{secFree}.
These results hold for the total, in and out degrees and strengths.
Stable sizes are also observed for 100 or less messages if classification of the three sectors is performed with one of the compound criteria established in Section~\ref{sectioning}. 
The networks often hold their basic structure with as few as 10-50 messages,
i.e. concentration of activity and the abundance of low-activity participants take place even with very few messages,
which is highlighted in Section~\ref{si:frac} of the Supporting Information document.
A minimum window size for the observation of more general properties might be inferred by monitoring 
both the giant component and the degeneration of the Erd\"os sectors.

In order to support hypotheses about the generality of these findings,
we expose the Erd\"os sector sizes of 12 networks from Facebook, Twitter and Participabr
in Table~\ref{tab:secE} of the Supporting Information document.
The fractions of hubs, intermediary and periphery nodes are essentially the same as for the email lists.

@@

\begin{table}[h]
	\caption{Distribution of activity among participants. The first column presents the percentage of messages sent by the most active participant. The column for the first quartile ($1Q$) shows the minimum percentage of participants responsible for at least 25\% of total messages. Similarly, the column for the first three quartiles $1-3Q$ gives the minimum percentage of participants responsible for 75\% of total messages. The last decile $-10D$ column exposes the maximum percentage of participants responsible for 10\% of messages.}
	\begin{center}
		\begin{tabular}{ | l ||  c | c | c | c | }
			\hline
			list & hub & $ 1Q $ & $ 1-3Q $ & $-10D$ \\ \hline
			\input{tables/userTab}
		\end{tabular}
	\end{center}
	\label{autores}
\end{table}

>>>>

The distribution of vertices in the hubs, intermediary, periphery Erd\"os sectors 
is remarkably stable along time is samples of 200 or more messages,
as evident in Figure~\ref{fig:sectIL} of current document
and in Section~\ref{si:frac} of the Supporting Information document. 
%Moreover, all email lists analyzed exhibit the same distribution profile.
Activity is highly concentrated on the hubs,
while a very large number of peripheral vertices contribute to only a fraction of the activity.
This is expected for a system with a scale-free profile
and confirmed by Table~\ref{autores} in the distribution of activity among participants.

Typically, $\approx [3-12]\%$ of the vertices are hubs,
$\approx [15-45]\%$ are intermediary and $\approx [44-81]\%$ are peripheral,
which is consistent with the literature~\cite{secFree}.
These results hold for the total, in and out degrees and strengths.
Stable sizes are also observed for 100 or less messages if classification 
of the three sectors is performed with one of the compound criteria established in Section~\ref{sectioning}. 
The networks often hold this basic structure with as few as 10-50 messages,
i.e. concentration of activity and the abundance of low-activity participants take place even with very few messages,
which is highlighted in Section~\ref{si:frac} of the Supporting Information document.
A minimum window size for the observation of more general properties might be inferred by monitoring 
both the giant component and the degeneration of the Erd\"os sectors.

In order to support hypotheses about the generality of these findings,
we expose the Erd\"os sector sizes of 12 networks from Facebook, Twitter and Participabr
in Table~\ref{tab:secE} of the Supporting Information document.
The fractions of hubs, intermediary and periphery nodes are
essentially the same as for the email list networks but with exceptions and a greater variability.

@@

\begin{table}[h]
	\caption{Distribution of activity among participants.
The first column presents the percentage of messages sent by the most active participant.
The column for the first quartile ($1Q$) exposes 
the minimum percentage of participants
responsible for at least 25\% of total messages with the actual number in parenthesis.
Similarly, the column for the first three quartiles $3Q$
gives the minimum percentage of participants responsible for 75\% of total messages.
The last decile $-10D$ column exposes the maximum percentage of participants responsible for 10\% of messages.}
	\begin{center}
		\begin{tabular}{ | l ||  c | c | c | c | }
			\hline
			list & hub & $ 1Q $ & $ 3Q $ & $-10D$ \\ \hline
			\input{tables/userTab}
		\end{tabular}
	\end{center}
	\label{autores}
\end{table}
